---
title: '...Processing ADR Data...'
output:
  # pdf_document: default
  html_document:
    df_print: paged
params:
  year:
    label: Year
    value: 2022
    input: numeric
    min: 2000
    max: 2099
    step: 1
  quarter:
    label: Quarter
    value: 1
    input: numeric
    min: 1
    max: 4
    step: 1
editor_options:
  chunk_output_type: console
---

<!-- ADR Report: Centers for Gastroenterology

This script combines client provided records of screening colonoscopies with 
LigoLab records of biopsies and assembles a dataset that is used to label 
each record as a screening colonoscopy, tubular adenomoa, serrated adenoma, 
malignancy, or needing manual interpretation. After manually verifying the 
output, the combined data are used by the Rmarkdown script to produce the ADR 
for the client.  -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r load libraries, include=FALSE}
library(tidyverse)
library(lubridate)
library(here)
```


```{r import clean client data, include=FALSE}
# Client data provided by CFG -----
client_raw <-
  list.files(path = here("data"),
             pattern = "(\\d){4}\\D\\d-\\D\\d{2}\\.\\d+\\.csv",
             full.names = TRUE) %>%
  sapply(readr::read_csv, simplify = FALSE) %>%
  bind_rows()

client_clean <-
  client_raw %>%
  mutate(
    dob_client = mdy(`Date of Birth`),
    match_name = str_extract(client_raw$`Patient Name`, "^.*,\\s..."),
    provider = `Provider Name`,
    dos_client = date(mdy_hm(`Exam Date`)),
    age = as.period(interval(start = dob_client, end = dos_client))$year
  ) %>%
  rename(sex = Gender) %>%
  filter(age >= 50) %>%
  select(provider, match_name, dos_client, dob_client, age, sex)
```


```{r import clean LigoLab data, include=FALSE}
ligo_raw <-
  list.files(path = here("data"),
             pattern = "(\\d){4}\\D\\d-ligo",
             full.names = TRUE) %>%
  sapply(readxl::read_excel, simplify = FALSE) %>%
  bind_rows()

# Filter data to include relevant locations/clients
#   - CFG Harmony, CFG Process at Summit, and Harmony Surgery Center)

# Filter cases performed for CFG Harmony Surgery Center -----
# client is CFG (HARMONY), CFG (PROESS AT SUMMIT), or HARMONY SURGERY CENTER
ligo_harmony <-
  ligo_raw %>%
  filter(str_detect(
    client,
    regex("cfg \\(h.*|cfg \\(p|harmony surgery.*", ignore_case = TRUE)
  ))

# separate provider last name, patient name to title case, filter age >= 50 
ligo_clean <-
  ligo_harmony %>%
  mutate(
    dob_ligo = mdy(dob),
    dos_ligo = mdy(dos),
    age = as.period(interval(start = dob_ligo, end = dos_ligo))$year,
    match_name = str_to_title(name),
    provider = str_to_title(doctor),
    colon = grepl("colon", diagnosis, ignore.case = TRUE)
  ) %>%
  separate(provider,
           c("provider", "f_name"),
           sep = " ",
           extra = "drop") %>%
  filter(age >= 50, colon == TRUE) %>%
  select(-c(age, sex, provider, dob, dos, client, doctor, name, f_name, colon))
```


```{r merge datasets, include=FALSE}
# Resulting dataset includes **all** screening colonoscopies
colonoscopy <-
  client_clean %>%
  left_join(ligo_clean,
            by = c("match_name" = "match_name", "dos_client" = "dos_ligo")) %>%
  mutate(yr = year(dos_client),
         qtr = quarter(dos_client)) %>%
  filter(yr == params$year & qtr == params$quarter)
```


```{r classify adenomas, include=FALSE}
neg_results <-
  str_c(
    c(
      "negative for definitive dysplasia and malignancy", 
      "negative for hyperplastic and adenomatous change",
      "negative for adenomatous change and malignancy",
      "negative for high-grade dysplasia",
      "negative for high grade dysplasia",
      "negative for high-grade dysplasia and malignancy",
      "negative for high grade dysplasia and malignancy",
      "negative for malignancy",
      "negative for dysplasia", 
      "negative for dysplasia and malignancy",
      "negative for adenomatous epithelium",
      "negative for active gastritis",
      "no invasive carcinoma",
      "no invasive adenocarcinoma",
      "no definitive carcinoma",
      "no definite invasive carcinoma",
      "no high-grade dysplasia or carcinoma",
      "no high-grade dysplasia or invasive carcinoma",
      "negative for intestinal metaplasia, dysplasia, and carcinoma",
      "negative for intestinal metaplasia, dysplasia and carcinoma",
      "negative for high-grade dysplasia and invasive carcinoma",
      "negative for dysplasia and carcinoma", 
      "negative for diagnostic features of sessile serrated adenoma, conventional adenoma and malignancy", 
      "negative for diagnostic features of hyperplastic polyp, sessile serrated adenoma, conventional adenoma and malignancy", 
      "negative for polyp, active colitis, microscopic colitis, granulomas, dysplasia and malignancy"
    ),
    collapse = "|"
  )

colon_class <-
  colonoscopy %>%
  mutate(
    diagnosis =
      str_replace_all(diagnosis, regex(neg_results, ignore_case = TRUE),
                      "xxxxx"),
    TA = str_detect(diagnosis, fixed("tubul", ignore_case = TRUE)) |
      str_detect(diagnosis, fixed("villous", ignore_case = TRUE)),
    SSA = str_detect(diagnosis, fixed("serrated", ignore_case = TRUE)),
    negative = str_detect(diagnosis, fixed("negative", ignore_case = TRUE)),
    carcinoma = str_detect(diagnosis, fixed("carcinoma", ignore_case = TRUE)),
    category = case_when(
      diagnosis %in% NA ~ "screen",
      carcinoma == TRUE ~ "evaluate",
      TA == TRUE  & SSA == FALSE ~ "ta",
      TA == FALSE & SSA == FALSE ~ "screen",
      TA == TRUE  & SSA == TRUE & negative == FALSE ~ "ta_ssa",
      TA == FALSE & SSA == TRUE & negative == FALSE ~ "ssa",
      TA == TRUE  & SSA == TRUE & negative == TRUE  ~ "evaluate",
      TA == FALSE & SSA == TRUE & negative == TRUE  ~ "evaluate",
      TRUE ~ "check_code"
    )
  ) 
```


```{r write files, include=FALSE}
# write data to Excel file and manually evaluate unresolved classifications
writexl::write_xlsx(colon_class, here(
  "output",
  paste0(params$year, "q", params$quarter,
         "-ADR-review.xlsx")
))

# write file containing all screening colonoscopies if requested by Dr. Sears
writexl::write_xlsx(colonoscopy, here(
  "output",
  paste0(params$year, "q", params$quarter,
    "-colonoscopies-CFG-Harmony.xlsx"
  )
))
```
---
## All data were processed successfully!


### 1) Go to the project ouput folder and open:

> `r params$year`q`r params$quarter`-ADR-review.xlsx

### 2) Manually review and score cases where

> "category" = "evaluate"

#### Filter the "category" column to show cases scored as "evaluate"  

**Read the diagnosis and score as one of the options below**  

|Category  | Definition |  
|----------|------------|  
|ta        | tubular adenoma present |  
|ta_ssa    | tubular and serrated adenoma present |  
|ssa       | serrated adenoma present |  
|carcinoma | carcinoma or malignancy present |  
|screen    | negative for all of the above |  

### 3) Save the revised file to the project data folder as:

> `r params$year`q`r params$quarter`-ADR-scored.xlsx

### 4) Knit the "02-CFG-ADR-Report.RMD" R markdown file to produce ADR Reports

- Be sure to knit with parameters and choose the year and quarter
- Send the completed report to Dr. Sears (ssears@digestive-health.net)
